---
title: 'Appendix: Code and Results'
output:
  word_document: default
---
#Packages needed
```{r, message=FALSE}
library(forecast)
library(zoo)
library(plyr)
library(urca)
library(rugarch)
library(pander)
```

#Load Data
```{r}
SP500.raw <- read.csv("../data/S&P500.csv")
VIX.raw <- read.csv("../data/Vix.csv")
ReVol.raw <- read.csv("../data/RealizedVol.csv")
```

```{r}
#Relized Volatility time series
ReVol.df <- ReVol.raw[-(1:2),1:2]
colnames(ReVol.df) <- c("Date", "Vol")
ReVol.df$Date <- as.Date(ReVol.df$Date, format = "%Y%m%d")
ReVol.df$Vol <- sqrt(as.numeric(as.character(ReVol.df$Vol)))
ReVol.df<- ReVol.df[!is.na(ReVol.df$Vol),]
ReVol.ts <- zoo(ReVol.df$Vol, ReVol.df$Date)

#SP500 Close Price time series
dates.sp <- as.Date(SP500.raw$Date,format="%Y-%m-%d")
SP500.ts <- zoo(SP500.raw$Adj.Close,dates.sp)

# SP500 Return time series
SPret.ts <- diff(log(SP500.ts))

# Vix Index time series
dates.vix <- as.Date(VIX.raw$Date,format="%Y-%m-%d")
VIX.ts <- zoo(VIX.raw$Adj.Close,dates.vix)

# Align all Time Series 
startdate <- time(ReVol.ts)[1]
SPret.ts <- window(SPret.ts, start = startdate)
VIX.ts <- window(VIX.ts, start = startdate)
```

#Relized Volatility Forecasting
###Basic check for Relized Vol series
```{r, fig.keep="none" }
plot(ReVol.ts, ylim = c(0,0.06), cex.lab = 1.5, cex.main = 2,
     main = "SP500 Daily Realized Volatility (5-min Sub-sampled)",
     xlab = "Years",
     ylab = "Realized Volatility (Standard Deviation)")
```

```{r}
#Unit Root Test
ReVol.ur <- ur.df(ReVol.ts, type = "none", selectlags="BIC")
summary(ReVol.ur)
```

```{r, fig.keep="none" }
#ACF
Acf(as.numeric(ReVol.ts), cex.lab = 1.5, cex.main = 2, 
    main = "Autocorrelation Plot of SP500 Realized Vol")
#Pacf
Pacf(as.numeric(ReVol.ts),  cex.lab = 1.5, cex.main = 2,
     main = "Partial Autocorrelation Plot of SP500 Realized Vol")
```

###Data Preprocessing
```{r}
ma6.ts <-  rollmean(ReVol.ts, k=6, align="right")
Sign <- sign(SPret.ts) >0
ret_sign <- Sign * SPret.ts

lagvol <- cbind(ReVol.ts,
                lag(ReVol.ts,-1,na.pad=TRUE),
                lag(ReVol.ts,-2,na.pad=TRUE), 
                lag((ma6.ts),-2,na.pad=TRUE),
                SPret.ts,
                Sign,
                ret_sign)
colnames(lagvol) <- c("vol", "volL1", "volL2", "ma6L2","Return", "Sign", "Return*Sign")

lagvol <- lagvol[complete.cases(lagvol),]

# Data Partitioning
ReVol.tra <- window(lagvol, end = "2015-01-02")
ReVol.va <- window(lagvol, start = "2015-01-03")
```

###GRACH Model as Benchmark
```{r}
# Specifications
spec <- ugarchspec(variance.model=list(garchOrder=c(1,1)),
                   mean.model=list(armaOrder=c(0,0)))
fittrain <- ugarchfit(spec = spec, data=ReVol.tra$Return)

#forecast
setfixed(spec) <- as.list(coef(fittrain))
ugarchfilter <- ugarchfilter(spec=spec,data=ReVol.va$Return)

# fitted volatility
volfcast.grach<- zoo(sigma(ugarchfilter))

#Validation set Forecasting errors of GARCH Model
grach.acc <- accuracy(na.locf(as.ts(ReVol.va$vol)), na.locf(as.ts(volfcast.grach)))
```

```{r, fig.keep="none" }
plot(ReVol.va$vol, ylim = c(0,0.06), cex.lab = 1.5, cex.main = 2,
     main = "SP500 Realized Volatility vs Forecasted Vol from GARCH",
     xlab = "Years",
     ylab = "Volatility (Standard Deviation)")
lines(volfcast.grach, col="red")
```

### Benchmark Model For Relized Volatility
```{r}
#ARMA model
ReVol.arima <- auto.arima(zoo(ReVol.tra[,1], time(ReVol.tra)),d=0,ic="bic",seasonal=FALSE)
#Best Arima model is AR2
arima.ben <- lm(vol ~ volL1 + volL2,data=ReVol.tra)
# MIDAS model
midas.ben <- lm(vol ~ volL1 + ma6L2,data=ReVol.tra)


arima.ben.pre <- predict(arima.ben, ReVol.va)
arima.ben.res <- ReVol.va$vol- arima.ben.pre

midas.ben.pre <- predict(midas.ben, ReVol.va)
midas.ben.res  <- ReVol.va$vol- midas.ben.pre
```

```{r}
#Validation set Forecasting errors of AR2 Model
arima.ben.acc <- accuracy(arima.ben.pre, ReVol.va$vol)
arima.ben.acc
```

```{r}
#Validation set Forecasting errors of MIDAS Model
midas.ben.acc <- accuracy(midas.ben.pre, ReVol.va$vol)
midas.ben.acc 
```

```{r}
#Diebold/Mariano AR2 versus MIDAS
dm.test(na.locf(as.ts(arima.ben.res)), na.locf(as.ts(midas.ben.res)))
```

###Leverage Effect as Dummy
```{r}
midas.dummy <- lm(vol ~ volL1 + ma6L2 + Sign,data=ReVol.tra)
midas.dummy.pre <- predict(midas.dummy, ReVol.va)
midas.dummy.res <- ReVol.va$vol- midas.dummy.pre
```

```{r}
#Validation set Forecasting errors of MIDAS Model with Dummy Leverage Effect
midas.dummy.acc <- accuracy(midas.dummy.pre, ReVol.va$vol)
midas.dummy.acc
```

```{r}
#Diebold/Mariano MIDAS Model with Dummy Leverage Effect versus MIDAS Benchmark
dm.test(na.locf(as.ts(midas.dummy.res)), na.locf(as.ts(midas.ben.res)))
```

###Leaverage Effect as Return
```{r}
midas.return <- lm(vol ~ volL1 + ma6L2 + Return, data=ReVol.tra)
midas.return.pre <- predict(midas.return, ReVol.va)
midas.return.res <- ReVol.va$vol- midas.return.pre
```

```{r}
#Validation set Forecasting errors of MIDAS Model with Return
midas.return.acc <- accuracy(midas.return.pre, ReVol.va$vol)
midas.return.acc 
```

```{r}
#Diebold/Mariano MIDAS Model with Return versus MIDAS with dummy leverage effect
dm.test(na.locf(as.ts(midas.return.res)), na.locf(as.ts(midas.dummy.res)))
```

###Best Forecasting Model: Leverage effect as Return and Cross-product term with sign dummy
```{r}
midas.ret_sign <- lm(vol ~ volL1 + ma6L2 + Return + `Return*Sign`, data=ReVol.tra)
midas.ret_sign.pre <- predict(midas.ret_sign, ReVol.va)
midas.ret_sign.res <- ReVol.va$vol- midas.ret_sign.pre
```

```{r}
#Validation set Forecasting errors of MIDAS Model with Return and Dummy
midas.ret_sign.acc <- accuracy(midas.ret_sign.pre, ReVol.va$vol)
midas.ret_sign.acc
```

```{r}
#Diebold/Mariano MIDAS Model with Return and Dummy versus MIDAS with Return
dm.test(na.locf(as.ts(midas.ret_sign.res)), na.locf(as.ts(midas.return.res)))
```

```{r, results=FALSE}
RMSE <- rep(NA,6)
RMSE[1] <- grach.acc[2]
RMSE[2] <- arima.ben.acc[2]
RMSE[3] <- midas.ben.acc[2]
RMSE[4] <- midas.dummy.acc[2]
RMSE[5] <- midas.return.acc[2]
RMSE[6] <- midas.ret_sign.acc[2]

pander(data.frame(RMSE = RMSE, 
           row.names = c("GARCH Model",
                         "AR2 Benchmark",
                         "MIDAS Benchmark",
                         "Leverage Effect as Dummy  Model",
                         "Leverage Effect as Return Model",
                         "Leverage Effect with Return and Dummy  Model")))
```

```{r}
summary(midas.ret_sign)
```

#Final Conclusion
```{r, fig.keep="none" }
vix.plot <- window(VIX.ts, start = "2015-01-05")/sqrt(252)/100

plot(ReVol.va$vol, ylim = c(0,0.06), cex.lab = 1.5, cex.main = 2,
     main = "SP500 Realized Volatility and Forecastings vs Vix Index ",
     xlab = "Years",
     ylab = "Volatility (Standard Deviation)")
lines(volfcast.grach, col="red")
lines(zoo(midas.ret_sign.pre, time(ReVol.va$vol)), col="blue")
lines(vix.plot, col = "green")
legend("topright", 
       legend=c("Realized Vol", "GARCH Forecast", 
                "MIDAS with leverage effect forecast","Vix" ),
       col=c("black", "red", "blue", "green"),lty=1:1, cex=1.5)
```

#Potential Financial Applications
###Control Volatility
```{r, results=FALSE}
vol.fcast <- midas.ret_sign.pre
# set for 10 percent annual standard deviation
target <- 0.05/sqrt(252)
# now portfolio weight vector
weight <- target/vol.fcast

# dynamic portfolio (assuming 3 percent/year interest)
pret  <-  ReVol.va[,5]*weight  + 0.03/252 *(1-weight)
pretEquity   <-  ReVol.va[,5]* 1

# Volatility for portfolios (daily to annual)
pstd  <-  sqrt(252)*ReVol.va[,1]*weight
pstdEquity   <-  sqrt(252)*ReVol.va[,1]*1

sharp <- rep(NA,2)
ret.mean <- rep(NA,2)
ret.sd <- rep(NA,2)
sd.sd <- rep(NA,2)

ret.mean[1] <- mean(pret)*252
ret.mean[2] <- mean(pretEquity)*252
ret.sd[1] <- sd(pret)*sqrt(252)
ret.sd[2] <- sd(pretEquity)*sqrt(252)
sd.sd[1] <- sd(pstd)
sd.sd[2] <-sd(pstdEquity)
sharp <- (ret.mean-0.03)/ret.sd

pander(data.frame(SharpRatio = sharp,
                  MeanReturn = ret.mean,
                  SDReturn = ret.sd,
                  SDofSD = sd.sd,
                  row.names = c("Vol Control Method", "Direct Investment")))

```

```{r, fig.keep="none" }
plot(pstd,ylim=c(0,0.8), cex.lab = 1.5, cex.main = 2,
     main = "SP500 Realized Volatility vs Vol after Control ",
     xlab = "Years",
     ylab = "Annualized Std")
lines(pstdEquity,col="red")
grid()
```

